Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-12-29 paper/ms.tex
discussion section edited

We end up with $40$ consistent models, out of the initial set of
$9000$. To facilitate the discussion of these results we define a new
quantity, the halo mass range $\Delta M=\log_{10}M_{\rm max} -
\log_{10}M_{\rm  min}$. This quantity together with the occupation
fraction, $f_{\rm occ}$, and the minimum mass $M_{\rm min}$ allows us
to clasify all the successful models into three families:

\begin{itemize}
\item[(1)] Low $f_{\rm occ}\leq 0.2$, $M_{\rm min}\leq 10^{10.8}\hMsun$ and low $\Delta M\leq 1.0$
  dex: 16 models. 
\item[(2)] High $f_{\rm occ}> 0.2$, $M_{\rm min}\geq 10^{10.8}\hMsun$ and
  low $\Delta M\leq 1.0$: 17 models

\item[(3)] Models with low occupation $f_{\rm occ}\leq 0.2$ fraction
  and high $\Delta M>1.0$: 7 models
\end{itemize}

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. They have mean values of $\theta_0$
  outside the observational uncertainties in that parameter, but have
  been included as consistent because their error bars overlap. These
models they have another particular feature: their minimum mass is
$M_{\rm min}=10^{10.9}\hMsun$. In what follows we exclude these models
from the discussion.}

A complete parameter list for the three families is presented in Table
\ref{table:firstfamily}, Table \ref{table:secondfamily} and Table
\ref{table:thirdfamily}. There are two interesting feature in these
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$.

{\bf The existence of models with high occupation fractions $f_{\rm
    occ}>0.3$ is unexpected from previous clustering analysis that do
  not take  account the effect of cosmic variance in the same way we
  propose in this \documentname. It seems that taking explicitly into
  account  effect hinders the possibility of constraining the LAEs
  occupation fraction.}

{\bf This challenge can be tracked to the uncertainty in the minimum
  halo mass. Within out framework, high occupation fraction are
  allowed because there are models where the minimum mass for hosting
  observable LAEs is larger than $10^{10.8}$\hMsun, which are fully
  consistent with the observational constraints.}

{\bf On the other hand, a robust conclusion is that all
possible models have narrow mass range regardless of the occupation
fraction.}

...A cut at the low mass end, $M_{\rm min}$, can be
interpreted in terms of the minimal halo star formation rate needed to
produce the \ly luminosity needed to be above a given detection
threshold.  However, under the reasonable assumption of star formation
rate increasing with halo mass, the cut at higher halo masses $M_{\rm
  max}$requires a different justification. There are two complementary physical
scenarios that could provide it.

@@

\subsection{Comparison against results from galaxy surveys}

Theoretical interpretations of blind galaxy surveys at $z=2.2$ find a
volume weighted escape fraction $f_{\rm esc}\sim 0.1-0.2$
\cite{Hayes2010}, similar results are obtained in a recent theoretical
study of observational data in a wide redshift range $0<z<6$
\citep{Dijkstra2013}.

\cite{Hayes2010} showed that the luminosity function for
LAEs at $z=2.2$ is consistent with the escape fraction being constant
for every galaxy regardless of its luminosity. From this results they
derive that almost $90\%$ of the star forming galaxies emit insufficient
Lyman $\alpha$ to be detected, effectively setting the occupation
fraction to be $f_{\rm occ}=0.10$. \cite{Dijkstra2013} use similar
methods to find an average \ly escape fraction in high-z galaxies,
they conclude that there is a range in \ly luminosity where the escape
fraction they derive at $z\sim 3.0$, $f_{\rm esc}=(17\pm 5)\%$, could
be interpreted as an occupation fraction $f_{\rm occ}\sim 0.2$. We
consider a success that our model indeed includes such low occupation
fraction models. The observational evidence from galaxy surveys seem
to disfavor the second family of models with high occupation
fractions.

@@

Our results are in a general good agreement with those estimates for
the host mass. This is not completely unexpected given that we have
also required consistency with ACF measurements. These expectations
are matched by the first family of models, also summarized in Table
\ref{table:firstfamily}. These models, which favor only the very
low occupations fractions, are also consistent in that regards with
the observational expectations.

The novelty in our results is that we have a detailed estimate for 
host halo mass range together with the escape fraction. This allows us
to demonstrate that the halo mass range can in some cases be narrow $\Delta M <
0.3$dex, something that cannot be inferred from ACF analysis alone.
Furthermore, In contrast to \citep{Gawiser07} and \citep{Ouchi2010} we
find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.6 &11.7 & 0.1& 1.1 \\
 10.9 &12.0 & 0.2& 1.1 \\
 10.9 &12.1 & 0.2& 1.2 \\
 10.9 &12.2 & 0.2& 1.3 \\
 10.9 &12.3 & 0.2& 1.4 \\
 10.9 &12.6 & 0.2& 1.7 \\
 10.9 &12.8 & 0.2& 1.9 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the third
  family of models. Wide mass range $\Delta M> 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.2$.} 
\end{table}

>>>>

Out of the initial set of $9000$ models we end up with $40$ that are
consistent with the observational constraints. To facilitate the
discussion of these models we define a new quantity, the halo mass
range $\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm  min}$, which
together with the occupation fraction, $f_{\rm occ}$, and the minimum
mass $M_{\rm min}$ allows us to clasify all the successful models into
three families:

\begin{itemize}
\item[(1)] Low occupation fraction $f_{\rm occ}\leq 0.2$ and narrow
  mass range $\Delta M\leq 1.0$ 
  dex: 16 models. 
\item[(2)] High occupation fraction $f_{\rm occ}> 0.2$ and
  narrow mass range $\Delta M\leq 1.0$: 17 models 
\item[(3)] Low occupation fraction $f_{\rm occ}\leq 0.2$ 
  and wide mass range $\Delta M>1.0$: 7 models
\end{itemize}

A complete parameter list for the three families is presented in Tables
\ref{table:firstfamily}, \ref{table:secondfamily}  and 
\ref{table:thirdfamily}.

{\bf The models in the third family are barely consistent with the
  constraints from the ACF. They have mean values of $\theta_0$
  outside the observational uncertainties, but have
  are considered as consistent because their error bars overlap. These
  models they have another particular feature: their minimum mass is
  exactly $M_{\rm min}=10^{10.9}\hMsun$. Because these models are
  are barely compatible with observations and are a minority of the
  consisten models, we exclude them now from the discussion.}

There are two interesting feature in the remaining two first
families. First, the occupation fraction can take any value from $0.1$
to $1.0$. Second, the halos hosting LAEs all have a narrow mass range
$\Delta M\leq 1.0$.

{\bf The existence of models with high occupation fractions $f_{\rm
    occ}>0.2$ is unexpected from previous clustering analysis that do
  not take  account the effect of cosmic variance in the same way we
  propose in this \documentname. This suggests that taking explicitly
  cosmic variance into account hinders the possibility of constraining the LAEs
  occupation fraction.}

\subsection{Physical interpretations}

{\bf The occupation fraction is midly correlated with a model's
  minimum mass. As can be observed in the right panel of Figure 6, the
  majority of  models with a high occupation fraction have  a minimum
  mass $M_{\rm  min}> 10^{10.7}$\hMsun. Therefore, low values for the
  occupation fraction would be favored if one could rule out models
  with a minimum mass above that threshold.}

{\bf On the other hand, a robust conclusion from the two first families
  is that the possible models have a narrow halo mass range $\Delta M
  <1.0$. How can we give a physical interpretation to the existence of
a narrow mass range? We can start with a reasonable assumption of star
formation rate increases with halo's mass. In this way a narrow
$\Delta M$ implies a cut both at the low and high mass end. }

A cut at the low mass end, $M_{\rm min}$, can be
interpreted in terms of the minimal halo star formation rate needed to
produce the \ly luminosity needed to be above a given detection
threshold.   A cut at higher halo masses $M_{\rm  max}$ requires a
different justification. There are two complementary physical
scenarios that could provide it.

@@

@@

Our results are in a general good agreement with those estimates for
the host mass. This is not completely unexpected given that we have
also required consistency with ACF measurements. These expectations
are {\bf mostly} matched by the first family of models, also summarized in Table
\ref{table:firstfamily}. These models, which favor only the 
low occupations fractions, are also consistent in that regards with
the observational expectations.

The novelty in our results is that we have a detailed estimate for 
host halo mass range together with the escape fraction. This allows us
to show that the halo mass range can, in some cases, be narrow $\Delta M <
0.3$dex, something that cannot be inferred from ACF analysis alone.
Furthermore, In contrast to \citep{Gawiser07} and \citep{Ouchi2010} we
find that an ACF analysis on a single data-set is not enough to rule
out models with a high occupation fraction $f_{\rm occ}>0.3$, which
represent half of our best models.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
 10.6 &11.7 & 0.1& 1.1 \\
 10.9 &12.0 & 0.2& 1.1 \\
 10.9 &12.1 & 0.2& 1.2 \\
 10.9 &12.2 & 0.2& 1.3 \\
 10.9 &12.3 & 0.2& 1.4 \\
 10.9 &12.6 & 0.2& 1.7 \\
 10.9 &12.8 & 0.2& 1.9 \\\hline
\end{tabular}
\end{center}
\caption{\label{table:thirdfamily}List of parameters for the third
  family of models. Wide mass range $\Delta M> 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.2$. {\bf These models are barely
  consistent with the constraints from the Angular Correlation
  Function and have been excluded from the main discussion.}} 
\end{table}
